### 2018-10-12 paper/paper.tex
Updates to acknowledgements per Stu's suggestion

\section*{Acknowledgments}
The authors would like to thank Matthew T. Harrison and Yang Chen for helpful discussions and Charles Lawrence for valuable comments and suggestions. This work was partially supported by the Office of Naval Research under Contract ONR N000141613168.

>>>>

\section*{Acknowledgments}
The authors would like to thank Yang Chen for helpful discussions and Matthew T. Harrison and Charles Lawrence for many valuable suggestions. This work was partially supported by the Office of Naval Research under Contract ONR N000141613168.
